---
title: "Puru Vaish s2236141 HWA 2"
output: html_notebook
---
**Q**  
g)  Read the data set in the supplementary file athletes.csv into the statistical software R. Estimate the probability in part e. by replacing μ and σ by the corresponding MLE and compute the confidence intervals in part f. (The best would be if you print the R script and attach it to your homework).

```{r Initialise_all_the_variables}
# If the file is in the same directory
setwd("./")
athlete_df = read.csv("athletes.csv")
# Else:
# athlete_df = read.csv(file.choose())

#get the names of the column for reference
print(names(athlete_df))

# Register the names of the header into R workspace
attach(athlete_df)

# the number of values in the data set before dropping na
n = length(TEratios)

# Clean athlete data if there are any na values in TEratios
if (sum(TEratios == F) != 0) {
  athlete_df = athlete_df[!which(is.na(TEratios))]
}

# the number of values in the data set after dropping na
n = length(TEratios)

# calculate the mean of the data set, I explicitly used the mle formula, even though R uses the same mean just to be explicit
mu_mle = sum(TEratios)/n

# calculate the sigma (standard deviation) using the variance formula. I had to use the formula here explicitly since R uses n-1, which is not the case for mle of sigma_sq
sigma_mle = sqrt(sum((TEratios-mu_mle)^2)/n)
```

**Q.**  
Estimate the probability in part e. by replacing μ and σ by the corresponding MLE
```{r}
prob = 1 - pnorm(4, mean = mu_mle, sd = sigma_mle)
sprintf(" The probability a 'clean' athlete has suspicious ratio is= %f", prob)
```
**Q**  
compute the confidence intervals in part f
for mu_mle
```{r}
c_0.025 = qnorm(1-0.025, df=n-1)
mu_mle_ci_0.025 = c(mu_mle - c_0.025*(sigma_mle)/sqrt(n), mu_mle + c_0.025*(sigma_mle)/sqrt(n))
sprintf("for mu_mle The lower bound is: %f and the upper bound is: %f for confidence interval 95", mu_mle_ci_0.025[1], mu_mle_ci_0.025[2])
```
for sigma_mle
```{r}
c_0.05_1 = qchisq(1-0.05, n-1)
c_0.05_2 = qchisq(0.05, n-1)

sigma_mle_ci_0.05 = c(sqrt(n*(sigma_mle^2)/c_0.05_1), sqrt(n*(sigma_mle^2)/c_0.05_2))
sprintf("for sigma_mle The lower bound is: %f and the upper bound is: %f for confidence interval 90", sigma_mle_ci_0.05[1], sigma_mle_ci_0.05[2])
```

